Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-11-04 text/paper/paper2.tex
Descriptive results: tfs.

Participants' judgments are depicted in Figures \ref{Fig:EC_judgments} and 
\ref{Fig:LC_judgments}. Judgments were coded as \ec, \lc if they were as expected
under one of these readings, and "other" if they were not. The distributions 
of readings thus coded is illustrated in Figure \ref{fig:response-type-freque-TRF}

@@

\begin{itemize}
\item see Figure~\ref{fig:response-type-freque-TRF}
\end{itemize}

>>>>

Participants' judgments are depicted in Figures \ref{Fig:EC_judgments} and 
\ref{Fig:LC_judgments}. Judgments were coded as \ec or as \lc if they were as expected
under one of these readings, and as "other" if they were not. The distributions 
of readings thus coded is illustrated in Figure \ref{fig:response-type-freque-TRF}. 
Overall, participants mainly gave answers corresponding to the \lc-reading. Moreover,
the preference for this reading was constrained by prosody. When prosody supported 
a dispreferred \ec-reading, the number of \lc-decisions was decreased. The number 
of erroneous answers did not differ between the single conditions. Finally, the
availability of readings within a sequence did not yield any significant effects.

In both \lc- and \ec-sequences, the number of \lc-answers was highest when this reading
was supported by prosodic phrasing (i.e. 77\%  and 76\% , respectively), and a bit lower
with neutral prosody (69\%  and 63\% ). This clearcut advantage decreased when prosodic
phrasing supported the \ec-reading (52\%  vs. 56\% ).

In order to test statistically whether prosodic phrasing and the sequential ordering 
had an effect on the number of \lc choices, log-linear models with the factors
{\it Reading}, {\it Prosody}, {\it Sequence}, {\it Item}, and {\it Participant} were included.

An effect of {\it Reading} reflects that overall, readings were distributed inhomogeneously
($LRCS = 539.04, p < .001$). As revealed by an interaction between {\it Prosody} and
{\it Reading}, prosodic phrasing had an influence upon the distribution of readings 
($LRCS = 50.42, p < .001$). Finally, an interaction between {\it Participant} and {\it Reading}
shows that readings were distributed unevenly amongst participants ($LRCS = 345.22, p < .001$)

@@

%\begin{itemize}
%\item see Figure~\ref{fig:response-type-freque-TRF}
%\end{itemize}
